Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-03 paper.tex
Abstract says 'are faster' instead of 'may be faster'
Abstract sums up results

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  This paper investigates whether using
Boolean operations may be faster in the simple case where two axis-aligned
volumes intersect.
\end{abstract}

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  This paper investigates whether using
Boolean operations are faster in the simple case where two axis-aligned volumes
intersect.  Although viable options it is shown that two new methods are only as
fast or no faster than the traditional slicing method.
\end{abstract}
